Cultural Transmission Can Explain the Evolution of Cooperative Behavior

### 2020-07-13 ms/main.tex
add more comment

\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2a.pdf}
    \caption{$V=1$, $T_A=T_B=T$, $\alpha \neq 0$}
    \label{fig:results_a}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2b.pdf}
    \caption{$V=1$, $\alpha = 0$}
    \label{fig:results_b}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2c.pdf}
    \caption{$V=0$}
    \label{fig:results_c}
  \end{subfigure}
  \label{fig:results}
  \caption{numerical results}
\end{figure}

>>>>

\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$. % DC: I didn't show it but it applies

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2a.pdf}
    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
    \label{fig:results_a}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2b.pdf}
    \caption{$v=1$, $\alpha = 0$}
    \label{fig:results_b}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2c.pdf}
    \caption{$v=0$}
    \label{fig:results_c}
  \end{subfigure}
  \label{fig:results}
  \caption{Numerical results of different scenarios. $\tilde{p}$ is ploted against time (generations) in (a) and (b), where $\tilde{p}$ is the frequency of parents with phenotypes A (cooperators) among the population. \\ $p'$ is ploted against time (generations) in (c). In each figure, the green line presnt the condition for fixation of cooperation, the orange line is equilibria and green is fixation of defectors}
\end{figure}
